
---
title: "Growers report"
author: "JCSIRO team"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document: default
---

```{r setup and load library, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(dplyr)
library(tidyverse)
library(readr)
library(lubridate)
library(DT)
library(sp)


library(rgdal)
library(sf)

#install.packages("plotKML")
library(plotKML)
library(knitr)
library(png)

library(readxl)


library(ggmap)
library(maps)
library(mapdata)

library(raster)
library(formattable)
library(magick)
library(readxl)

```

## Growers and details
```{r define_sites, echo=FALSE, message=FALSE, warning=FALSE}



#######################################################################################################################################################
paddock_done2020_t<- read_excel("C:/Users/ouz001/CSIRO/Ratcliff, Christina (A&F, Waite Campus) - Soil_Testing_Project/paddock_done2020.xlsx", 
                              sheet = "T-test_done")

paddock_done2020_t <- paddock_done2020_t %>% 
  dplyr::mutate(paddock5_digits = substr(`Paddock code`, start = 1, stop = 5))

#select orgaiastion

selection_organisation <- "Agrivision"

paddock_done2020 <- 
  filter(paddock_done2020_t, Organisation %in% selection_organisation) %>% 
    distinct(paddock5_digits, .keep_all= TRUE) %>% 
    dplyr::select(paddock = paddock5_digits,
                  Organisation,
                  Contact,
                  Farmer,
                  `Paddock tested`,
                  'issues/ comments',
                  'Rates excluded' = Rates_excluded)  

paddock_done2020_display <- 
  filter(paddock_done2020_t, Organisation %in% selection_organisation) %>% 
    distinct(paddock5_digits, .keep_all= TRUE) %>% 
    dplyr::select(Paddock = paddock5_digits,
                  Organisation,
                  Contact,
                  Farmer,
                  `Paddock tested`,
                  'issues/ comments')  

paddock_done2020_display %>% 
   formattable(align = "l", - 1  )


```



```{r define_sites2, echo=FALSE, message=FALSE, warning=FALSE}


## set up some folder to look for data:

png_folder <- "W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/png"

Growers_folder <- paste0("W:/value_soil_testing_prj/Yield_data/2020/", 
unique(paddock_done2020$Organisation), "/",unique(paddock_done2020$Contact), "/")


Growers_folder <- gsub(" ", "_", Growers_folder)
Growers_folder <- gsub("-", "_", Growers_folder)



#each folder for the sites (4 listed here)
site1 <- paste0((unique(paddock_done2020$Farmer)[1]),"/",
                (unique(paddock_done2020$`Paddock tested`)[1]),
                "/output/")
                
site2 <- paste0((unique(paddock_done2020$Farmer)[2]),"/",
                (unique(paddock_done2020$`Paddock tested`)[2]),
                "/output/")

site3 <- paste0((unique(paddock_done2020$Farmer)[3]),"/",
                (unique(paddock_done2020$`Paddock tested`)[3]),
                "/output/")

site4 <- paste0((unique(paddock_done2020$Farmer)[4]),"/",
                (unique(paddock_done2020$`Paddock tested`)[4]),
                "/output/")

site1 <- gsub(" ", "_", site1)
site1 <- gsub("-", "_", site1)
site2 <- gsub(" ", "_", site2)
site2 <- gsub("-", "_", site2)
site3 <- gsub(" ", "_", site3)
site3 <- gsub("-", "_", site3)
site4 <- gsub(" ", "_", site4)
site4 <- gsub("-", "_", site4)



#Lets look for a yld trace maps

#list files that conatin the word "trace" followed by anything and ending with the word ".png":
yld_trace_site1 <- list.files(path = paste0(Growers_folder, site1),pattern = "trace(.*).png$", ignore.case = TRUE)
yld_trace_site2 <- list.files(path = paste0(Growers_folder, site2),pattern = "trace(.*).png$", ignore.case = TRUE)
yld_trace_site3 <- list.files(path = paste0(Growers_folder, site3),pattern = "trace(.*).png$", ignore.case = TRUE)
yld_trace_site4 <- list.files(path = paste0(Growers_folder, site4),pattern = "trace(.*).png$", ignore.case = TRUE)

#list files that conatin the word "harvest" followed by anything and ending with the word ".png": and excluding pre (2 steps)


harvest_pre_post_site1 <- list.files(path = paste0(Growers_folder, site1),pattern = "harvest(.*).png$", ignore.case = TRUE)
harvest_pre_post_site2 <- list.files(path = paste0(Growers_folder, site2),pattern = "harvest(.*).png$", ignore.case = TRUE)
harvest_pre_post_site3 <- list.files(path = paste0(Growers_folder, site3),pattern = "harvest(.*).png$", ignore.case = TRUE)
harvest_pre_post_site4 <- list.files(path = paste0(Growers_folder, site4),pattern = "harvest(.*).png$", ignore.case = TRUE)

harvest_map_site1 <- grep(harvest_pre_post_site1, pattern = 'pre', invert=TRUE, value=TRUE)
harvest_map_site2 <- grep(harvest_pre_post_site2, pattern = 'pre', invert=TRUE, value=TRUE)
harvest_map_site3 <- grep(harvest_pre_post_site3, pattern = 'pre', invert=TRUE, value=TRUE)
harvest_map_site4 <- grep(harvest_pre_post_site4, pattern = 'pre', invert=TRUE, value=TRUE)



### paddock id details
site_name_1 <- paste0("^",paddock_done2020$paddock[1])
site_name_2 <- paste0("^",paddock_done2020$paddock[2])
site_name_3 <- paste0("^",paddock_done2020$paddock[3])
site_name_4 <- paste0("^",paddock_done2020$paddock[4])




Paddock_selected_site1 <- paddock_done2020$paddock[1]
Paddock_selected_site2 <- paddock_done2020$paddock[2]
Paddock_selected_site3 <- paddock_done2020$paddock[3]
Paddock_selected_site4 <- paddock_done2020$paddock[4]





```

```{r read spatial data, message=FALSE, warning=FALSE, include=FALSE}
spatial_data_no_yld <- st_read("W:/value_soil_testing_prj/Yield_data/2020/All_Strips_2020_wgs84.shp")
spatial_data_no_yld_df <- data.frame(spatial_data_no_yld)
spatial_data_no_yld_df <- spatial_data_no_yld_df %>% dplyr::select(-geometry)

```

# Site 1

### Harvest map

```{r display site 1, echo=FALSE, message=FALSE, warning=FALSE}

include_graphics(paste0(Growers_folder,site1,  harvest_map_site1))
```


### Yield trace

```{r display site 1 yld trace, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(paste0(Growers_folder,site1,  yld_trace_site1))
```

### Results


```{r display results site 1, echo=FALSE, message=FALSE, warning=FALSE}

image_read(dir(png_folder, full.names=T, pattern=site_name_1)) %>% 
  image_rotate(90)

```







# Site 2

### Harvest map

```{r display site 2, echo=FALSE, message=FALSE, warning=FALSE}

include_graphics(paste0(Growers_folder,site2,  harvest_map_site2))
```

### Yield trace

```{r display site 2 yld trace, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(paste0(Growers_folder,site2,  yld_trace_site2))
```

### Results

```{r display results site 2, echo=FALSE, message=FALSE, warning=FALSE}

image_read(dir(png_folder, full.names=T, pattern=site_name_2)) %>% 
  image_rotate(90)

```


# Site 3

### Harvest map

```{r display site 3, echo=FALSE, message=FALSE, warning=FALSE}

include_graphics(paste0(Growers_folder,site3,  harvest_map_site3))
```

### Yield trace

```{r display site 3 yld trace, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(paste0(Growers_folder,site3,  yld_trace_site3))
```

### Results

```{r display results site 3, echo=FALSE, message=FALSE, warning=FALSE}

image_read(dir(png_folder, full.names=T, pattern=site_name_3)) %>% 
  image_rotate(90)

```


# Site 4

### Harvest map

```{r display site 4, echo=FALSE, message=FALSE, warning=FALSE}

include_graphics(paste0(Growers_folder,site4,  harvest_map_site4))
```

### Yield trace

```{r display site 4 yld trace, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(paste0(Growers_folder,site4,  yld_trace_site4))
```

### Results

```{r display results site 4, echo=FALSE, message=FALSE, warning=FALSE}

image_read(dir(png_folder, full.names=T, pattern=site_name_4)) %>% 
  image_rotate(90)

```


# Checks for CSIRO 

### check the rate provided is equavlient to the calulated N/P contnet.

```{r checks site , echo=FALSE, message=FALSE, warning=FALSE}

fert_applied <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_select_clm.csv")

check_fert_applied <- fert_applied %>%
  dplyr::filter(
    Paddock_ID == Paddock_selected_site1 |
      Paddock_ID == Paddock_selected_site2 |
      Paddock_ID == Paddock_selected_site3 |
      Paddock_ID == Paddock_selected_site4
  ) %>%
  dplyr::select(Paddock_ID,
                Rate,
                Strip_Rate,
                Strip_Type,
                Total_sum_N_content,
                Total_sum_P_content) %>%
  arrange(Paddock_ID, Rate)


check_fert_applied$Total_sum_N_content <- round(check_fert_applied$Total_sum_N_content, 2)
check_fert_applied$Total_sum_P_content <- round(check_fert_applied$Total_sum_P_content, 2)



check_fert_applied %>% 
  formattable(align = "l", - 1  )
```

## Comments from the spatial data

```{r comments on spatial data 2, echo=FALSE, message=FALSE, warning=FALSE}


comments_frm_spatial_data <- spatial_data_no_yld_df %>% 
  dplyr::filter(
    Paddock_ID == Paddock_selected_site1 |
      Paddock_ID == Paddock_selected_site2 |
      Paddock_ID == Paddock_selected_site3 |
      Paddock_ID == Paddock_selected_site4
  ) %>%
distinct( Comments, .keep_all = TRUE) %>% 
  dplyr::select(Paddock_ID ,Comments )

comments_frm_spatial_data %>% 
  formattable(align = "l", - 1  )
```

# Comparision of yield response: Growers standard practice strips (GSP vs Alt GSP)

The best outcome would be that the yield response in no response.

Or if there was a yield response between the two strips they would be not significant.

positive or negative yield resposnes that are significant suggest that there is a high degree of variability between the two strip that were applied with the same fertiliser.

This may occur beacuse the strips have underlying soil, plant growth conditions.


```{r plot2 alt strips results, echo=FALSE, message=FALSE, warning=FALSE}
GSP_AltGSP_t_test <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/GSP_AltGSP_t_test_merged_3c.csv")

GSPvsAltGSP_plot <- GSP_AltGSP_t_test %>%
  dplyr::filter(
    paddock_ID == Paddock_selected_site1 |
      paddock_ID == Paddock_selected_site2 |
      paddock_ID == Paddock_selected_site3 |
      paddock_ID == Paddock_selected_site4
  ) %>%
  ggplot( mapping = aes(x=Significant ))+
  geom_bar() +
  facet_grid(.~ Strip_Type)+
  theme_bw()+
  labs(title = "Comparison of yield response in strips with the same fertiliser rate",
       subtitle = "Strip with growers standard practice vs alterative growers standard practice",
       y = "Count of zones with a significant difference",
       x = "result of t - test (GSP vs. Alt GSP)")

GSPvsAltGSP_plot







```


```{r table alt strips results, echo=FALSE, message=FALSE, warning=FALSE}
GSP_AltGSP_t_test <- GSP_AltGSP_t_test %>% 
  dplyr::filter(
    paddock_ID == Paddock_selected_site1 |
      paddock_ID == Paddock_selected_site2 |
      paddock_ID == Paddock_selected_site3 |
      paddock_ID == Paddock_selected_site4
  ) 

GSP_AltGSP_t_test <- GSP_AltGSP_t_test %>%  dplyr::select(Zone_ID ,yld_response, `mean difference` = rounded, Significant ) 

 GSP_AltGSP_t_test %>% 
   formattable(align = "l", - 1  )
```




# Comparision of yield response: High medium and low fertiliser rates

The below table shows what fertiliser rates were assigned to low medium and high fertiliser rates.



```{r what is defined as high low , echo=FALSE, message=FALSE, warning=FALSE}

                        
high_low_comp <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/hign_low_t_test_merged_3b.csv")



high_low_comp <- high_low_comp %>%
  dplyr::filter(
    paddock_ID == Paddock_selected_site1 |
      paddock_ID == Paddock_selected_site2 |
      paddock_ID == Paddock_selected_site3 |
      paddock_ID == Paddock_selected_site4
  )

high_low_comp_define <-distinct(high_low_comp,paddock_ID, .keep_all = TRUE  ) %>% 
  dplyr::select(paddock_ID, 
                'rate low' = rate_low,
                'rate medium' = rate_medium,
                'rate high' = rate_high,
                'rate very high' = rate_very_high)

high_low_comp_define %>% 
  formattable(align = "l", - 1  )
```


```{r high med low comparision, echo=FALSE, message=FALSE, warning=FALSE}

                        


high_low_comp$comparison <-
  factor(
    high_low_comp$comparison,
    levels = c("high_v_low", "high_v_medium", "medium_v_low"),
    labels = c(
      "high fert vs low fert",
      "high fert vs medium fert",
      "medium fert vs low fert"
    )
  )


high_low_plot <-
  ggplot(high_low_comp, mapping = aes(x = yld_response, fill = Significant)) +
  geom_bar() +
  facet_grid(Strip_Type ~ comparison)+ 
  theme_bw() +
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  scale_x_discrete(
    labels = c(
      "positive" = "positive",
      "no_response" = "no response",
      "negative" = "negative"
    )
  ) +
    labs(
    title = "Comparison of yield response in strips with different fertiliser rate",
    subtitle = "The yield response is classed as positive when higher rates of fertiliser result in higher yields",
    y = "Count of paddocks in yield response class",
    x = "yield response"
  )
high_low_plot

```


# Comparision of yield response: the growers fertilisers rate of application vs. higher or lower fertilisers rates.


Different comparisons are made between the growers standard practice and fertilisers strips for each zone.

Comparison of yield response in the strip / zone per paddock between:

- Growers standard practice GSP  vs low fertiliser rate (yield for GSP fert rate - yield for low fert rate)
- Growers standard practice GSP  fertiliser rate vs high fertiliser rate (yield for GSP fert rate - yield for high fert rate)


The yield response is classed as 'positive' when higher rates of fertiliser results in higher yields

The yield response is classed as 'no response' when higher rates of fertiliser results in no change in yields (this is defined as 0 +/- standard error)

The yield response is classed as 'negative' when higher rates of fertiliser results in lower yields.

T- test was also run for each comparison and the significant differences at p < 0.05 reported.
Note that some significant values are not reported for the zone, this may occur when there is not enough data points to run the t - test (although there is still have yield values to make a comparison). 


The below table details what rates were excluded from the anlaysis.
For sites with more than 3 rates one strip rate was exluded from the analysis.

If this should be a different rate and not the one excluded the analysis will need to be re - run.
Please make a note.


```{r  GSP vs high  low rates exluded, echo=FALSE, message=FALSE, warning=FALSE}


rates_exluded <- paddock_done2020 %>% 
  distinct(paddock, .keep_all= TRUE) %>% 
  dplyr::select(paddock ,
                `Paddock tested`,
                'issues/ comments',
                'Rates excluded' = `Rates excluded`)



rates_exluded %>% 
  formattable(align = "l", - 1  )


```

### not sure why the below wont run??


```{r GR comp high low plot, echo=FALSE, message=FALSE, warning=FALSE}

                      

GR_comparison <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/GSP_low_high_comparision_t_test_merged_3d.csv")
GR_comparison <- GR_comparison %>%
  dplyr::filter(
    paddock_ID == Paddock_selected_site1 |
      paddock_ID == Paddock_selected_site2 |
      paddock_ID == Paddock_selected_site3 |
      paddock_ID == Paddock_selected_site4
  )

GR_comparison_plot <-
  ggplot(GR_comparison, mapping = aes(x = yld_response, fill = Significant)) +
  geom_bar() +
  facet_grid(Strip_Type ~ comparison)+ 
  #labeller(Strip_Type = label_wrap_gen(width = 16 ),
  #         comparison = label_wrap_gen(width = 16))) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  scale_x_discrete(
    labels = c(
      "positive" = "positive",
      "no_response" = "no response",
      "negative" = "negative"
    )
  ) +
  labs(
    title = "Comparison of yield response for GSP vs higher/lower rates",
    subtitle = "The yield response is classed as positive when higher rates of fertiliser result in higher yields",
    y = "Count of paddocks in yield response class",
    x = "yield response"
  )

GR_comparison_plot



```

# Action required : 


1. Review that the results look sensible and nothing needs re running - are the reports ok to send off?

2. The fertiliser appplied has translated correctly to units of N or P.

3. Are the paddocks to be included in the ecomnics analysis?



Notes should be made in the below file:

[For Notes ]("C:/Users/ouz001/CSIRO/Ratcliff, Christina (A&F, Waite Campus) - Soil_Testing_Project/paddock_done2020.xlsx")
