---
title: "Soil_testing_outputs"
author: "Jackie Ouzman"
date: "11/02/2021"
output: html_document
---

```{r setup and load library, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Summary of trials we have

The first section is a sumary of the data we have.
The trial type 
Location of trials etc



```{r load_data, message=FALSE, warning=FALSE, include=FALSE}
fert_app_select_clm <- read.csv("W:/value_soil_testing_prj/Yield_data/analysis_strip_trials_April/economic_analysis2020_2021/fert_app_select_clm.csv")

spatial_data_no_yld <- read_csv("W:/value_soil_testing_prj/Yield_data/analysis_strip_trials_April/all_strips_centroid_2021-02-11.csv")


# note that this file was generated from spatial analysis and R code
# the R code / script is:

#"W:\value_soil_testing_prj\Yield_data\analysis_strip_trials_April\economic_analysis2020_2021\spatial_data_no_yld.R"
#"W:\value_soil_testing_prj\Yield_data\analysis_strip_trials_April\economic_analysis2020_2021\work_out_N_P_content_no_starter_TD.R"


```

## Summary of spatial data

This data is a summary of what paddocks implemented a N or P fertiliser trial.
For these paddocks, we were given spatial data that allowed us to create maps.
These pre harvest map contain:

- loaction of strips in paddock
- location of zone (zones are location that the soil sampling was done)
- legends which indicate how much fertiliser was applied (product and rate)



```{r pressure, echo=FALSE}
str(spatial_data_no_yld)

spatial_data_no_yld_ID_only <- spatial_data_no_yld %>% 
  distinct(Paddock_ID, .keep_all = TRUE) %>% 
  dplyr::select(Paddock_ID, Strip_Type, StripCount, Alt_GSP,av_rain )
  
  spatial_data_no_yld %>% 
  group_by(Paddock_ID, Strip_Type)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
